\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-09-19 papers/methods/paper.tex
Scaffolding out bbc comparison

\begin{table}
	\centering
	\caption{{\green Parameters defined in our model and a summary of their use. The parameters are broken into multiple sections, the top for parameters which are defined globally across all surveys, the second section for parameters which are defined for each survey, the third section are parameters which are defined for each supernova. The bottom section shows the observables (not parameters) that are the input data to the model.}}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\delta S$ & Selection effect deviation \\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		$s_c$ & Colour bias\\
		\hline
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\alpha_c$ & Skewness of colour population \\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
		$m_B$ & True flux\\
		$x_1$ & True stretch \\
		$c$ & True colour \\
		$z$ & True redshift \\
		$M_B$ & Derived absolute magnitude \\
		$\mu$ & Derived distance modulus \\
		\hline
		$\hat{m}_B$ & Measured flux\\
		$\hat{x}_1$ & Measured stretch \\
		$\hat{c}$ & Measured colour \\
		$C$ & Covariance on flux, stretch and colour \\
		$\hat{z}$ & Observed redshift \\
		$\hat{m}$ & Determined mass probability \\
		$\hat{p}$ & Determined outlier probability \\
		\hline
	\end{tabular}
\end{table}

@@

With the report summary statistics being biased and their uncertainty under-reported, we face a significant challenge in supernova cosmology. We must either correct the observables to remove the biases introduced by the intrinsic dispersion of the underlying population, or incorporate this dispersion into our model. We must also do this without assuming a specific dispersion model (either the {\gten} or {\celeven} model). We address this in our analysis in two ways - increasing the reported uncertainty, and allowing for a global shift in observed colour.

@@

Our second way of addressing the issues with under-reported uncertainty and biased summary statistics are to use fiducial simulations (discussed further in Section \ref{sec:selection}) to characterise the shift in the mean colour measured as a function of redshift. By comparing simulated true colour values to simulated observed colour values, we can quantify the mean bias in colour in redshift bins, giving us {\green a redshift-dependent array of biases. We can then add this into our data-set, and is included in our modelling by allowing a controlled subtraction of this shift from our observed data, where the amount of shift subtracted is dictated by parameter $s_c$. Specifically, allow the observed colour to shift by $c_{\rm new} = c_{\rm biased} - s_c \times {\rm bias}(z)$, where `bias$(z)$' is the binned mean colour bias determined with fiducial simulations. Unlike $\kappa_0$ and $\kappa_1$, which are redefined for each survey, $s_c$ represents a global shift in supernovae colour across all surveys. We place a uniform prior on $s_c$.} With the extra dispersion introduced from the $\kappa$ parameters addressing the under-reporting of error, shifting the mean colour address the non-Gaussianity introduced by chromatic smearing. We allow the amount of shift to be parametrised to account for different intrinsic scatter models where parameter $s_c$ controls the fraction of bias subtraction: 0 for no shift, up to 1 for the maximum shift found in simulations. The maximum shift was found to using the intrinsic scatter model from \citet{Chotard2011}, which has greater chromatic dispersion than the {\gten} model.

It is important to note that the effects being modelled and characterised by simulations here are features of the supernova population, not cosmological features, and so the choice of fiducial cosmology has negligible impact. Our fiducial cosmology is a Flat $\Lambda$CDM universe with $\Omega_m = 0.3$ and $H_0 = 70\kmsmpc$.

{\red MAKE SOME ILLUSTRATIVE PLOT FOR THIS SECTION}

@@

	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, right=4.33cm of mu] (MBobs) {$M_B$};
	% Survey nodes
	\node[latent, above=of sum, yshift=1cm,text width=2.7cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle,\rho,\sigma_{M_B}, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c, \kappa_0, \kappa_1$ };
	\node[latent, right=1.5cm of pop1, align=center] (sf) {$\Delta_i, \delta_i$};
	% Global nodes
	\node[latent, above=2cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=1.7cm of MBobs, text width=3cm, align=center]  (ab) {$\langle M_B \rangle, \alpha, \beta$, $\delta(0)$, \\$\delta(\infty)$, $s_c$, $\delta \mathcal{Z}_i$, $\delta S$};

@@

\begin{table}
	\centering
	\caption{Parameter Correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}

@@

Unfortunately, adding extra fit parameters to allow for shifting observables washes out cosmology, and applying a specific bias correction requires running a fiducial simulation (assuming cosmology, population and scatter model) and binning data. It is difficult to do whilst accounting for correlations with population and scatter model. This is compounded by the fact that bias corrections do not in general improve fits (increase the log posterior), and so are difficult to fit inherently. Colour bias corrections for the {\celeven} scatter model are included in our cosmology model, the strengths of which are controlled by a fit parameter, $s_c$, however neither the {\gten} nor {\celeven} simulation fits constrained this parameter, and thus the majority of bias in the {\celeven} fits remain. Works such as \citet{Kessler2017} show that bias corrections can be applied to supernovae datasets that can robustly handle multiple intrinsic scatter models, and future work will center on uniting these methodologies - incorporating better bias corrections that separate intrinsic scatter bias and non-Gaussian summary statistic bias from Malmquist bias, without having to precompute standardisation parameters and populations.

\begin{figure*}
	\begin{center}
		\includegraphics[width=\textwidth]{bulk_cor.pdf}
	\end{center}
	\caption{Parameter correlations for the combined fits to the 100 {\gten} scatter model simulations. We see that the primary correlations with $w$ enter through $\alpha$, $\beta$ and $\langle M_B \rangle$, as shown in Table \ref{tab:parameter_correlations}. Also visible in this figure are several other interesting relationships. $\beta$ is strongly anti-correlated with intrinsic dispersion $\sigma_{m_B}$ for both surveys (DES like and LowZ), with $\sigma_{m_B}$ showing strong anti-correlation with $\kappa^0_c$. This relationship is indeed expected - as $\kappa^0_c$ grows larger (more unexplained dispersion on the colour observation), the width of the supernova population in apparent magnitude space increases. As the fit prefers it to conform to the observed width of the distribution, the extra width in colour causes the inherent magnitude smearing amount to decrease. And with extra freedom on the observed colour from $\kappa^0_c$, $\beta$ shifts in response. The other striking feature in the plot are the strong correlation blocks in the bottom right and the anti-correlation stripes on the edges. These too are expected, for they show the relationship between the colour distributions mean value, its width and its skewness. As skewness or population width increases, the effective mean of the population shifts (see Appendix \ref{app:approx} for details), creating anti-correlation between skewness and the (Gaussian) mean colour population. Strong anti-correlation between the $\kappa_{c0}^0$ and $\kappa_{c0}^1$ (and positive fit values) shows that a finite non-zero extra colour dispersion is indeed preferred by our model.  Finally, we notice the blank cross in the middle of the figure, the result of four parameters. Firstly, the redshift-dependent extra colour dispersion for the LowZ simulation is negligible (due to the low redshift values), the bias correciton $s_c^0$ is unconstrained by our fits, and as the SNANA simulations do not include mass, we expect zero correlation across the mass step $\delta(0)$ and $\delta(\infty)/\delta(0)$ parameters. }
	\label{fig:bulk_cor}
\end{figure*}

Table \ref{tab:parameter_correlations} lists the fit correlations between our model fit parameters (excluding the LowZ band systematics, and Malmquist bias uncertainty parameters which had negligible correlation), showing (in order) cosmological parameters, standardisation parameters, population width and skewness parameters, intrinsic dispersion parameters, mass-step parameters, population mean parameters, SALT2 model systematics, dust systematic, global HST calibration systematic, peculiar velocity systematic, global redshift systematic and DES band magnitude and wavelength systematics. Figure \ref{fig:bulk_cor} show the full correlations between all non-systematic model parameters. As expected, $w$ bias is introduced primarily through incorrectly determined $\beta$, which itself is tied to the unexplained colour dispersion and biases in colour introduced by the unknown intrinsic scatter model. Other interesting correlations are shown and discussed in Figure \ref{fig:bulk_cor}, however none have as significant an impact on cosmology as $\beta$. Table \ref{tab:parameter_correlations} does show that $\langle M_B \rangle$ is strongly correlated with $w$, however it is recovered much more accurately than $\beta$. The band systematics for DES filters $g$, $r$ and $i$ also show significant correlation with $w$, highlighting the importance of minimising instrumental uncertainty.

For the sample size of the DES and LowZ supernova samples (of order 350 supernova), the bias from intrinsic scatter models is sub-dominant to the statistical uncertainty, as shown in Figure \ref{fig:bulk_posterior}. {\green For our full systematics model, the bias represents a deviation between $-0.3\sigma$ to $0.3\sigma$ depending on scatter model, and as such we will leave more complicated treatment of them for future work.}

@@

@@

>>>>

\begin{table}
	\centering
	\caption{{\green Parameters defined in our model and a summary of their use. The parameters are broken into multiple sections, the top for parameters which are defined globally across all surveys, the second section for parameters which are defined for each survey, the third section are parameters which are defined for each supernova. The bottom section shows the observables (not parameters) that are the input data to the model.}}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\delta S$ & Selection effect deviation \\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		%$s_c$ & Colour bias\\
		\hline
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\alpha_c$ & Skewness of colour population \\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
		$m_B$ & True flux\\
		$x_1$ & True stretch \\
		$c$ & True colour \\
		$z$ & True redshift \\
		$M_B$ & Derived absolute magnitude \\
		$\mu$ & Derived distance modulus \\
		\hline
		$\hat{m}_B$ & Measured flux\\
		$\hat{x}_1$ & Measured stretch \\
		$\hat{c}$ & Measured colour \\
		$C$ & Covariance on flux, stretch and colour \\
		$\hat{z}$ & Observed redshift \\
		$\hat{m}$ & Determined mass probability \\
		$\hat{p}$ & Determined outlier probability \\
		\hline
	\end{tabular}
\end{table}

@@

With the report summary statistics being biased and their uncertainty under-reported, we face a significant challenge in supernova cosmology. We must either correct the observables to remove the biases introduced by the intrinsic dispersion of the underlying population, or incorporate this dispersion into our model. We must also do this without assuming a specific dispersion model -- either the {\gten} or {\celeven} model.

@@

%Our second way of addressing the issues with under-reported uncertainty and biased summary statistics are to use fiducial simulations (discussed further in Section \ref{sec:selection}) to characterise the shift in the mean colour measured as a function of redshift. By comparing simulated true colour values to simulated observed colour values, we can quantify the mean bias in colour in redshift bins, giving us {\green a redshift-dependent array of biases. We can then add this into our data-set, and is included in our modelling by allowing a controlled subtraction of this shift from our observed data, where the amount of shift subtracted is dictated by parameter $s_c$. Specifically, allow the observed colour to shift by $c_{\rm new} = c_{\rm biased} - s_c \times {\rm bias}(z)$, where `bias$(z)$' is the binned mean colour bias determined with fiducial simulations. Unlike $\kappa_0$ and $\kappa_1$, which are redefined for each survey, $s_c$ represents a global shift in supernovae colour across all surveys. We place a uniform prior on $s_c$.} With the extra dispersion introduced from the $\kappa$ parameters addressing the under-reporting of error, shifting the mean colour address the non-Gaussianity introduced by chromatic smearing. We allow the amount of shift to be parametrised to account for different intrinsic scatter models where parameter $s_c$ controls the fraction of bias subtraction: 0 for no shift, up to 1 for the maximum shift found in simulations. The maximum shift was found to using the intrinsic scatter model from \citet{Chotard2011}, which has greater chromatic dispersion than the {\gten} model.

%It is important to note that the effects being modelled and characterised by simulations here are features of the supernova population, not cosmological features, and so the choice of fiducial cosmology has negligible impact. Our fiducial cosmology is a Flat $\Lambda$CDM universe with $\Omega_m = 0.3$ and $H_0 = 70\kmsmpc$.

%{\red MAKE SOME ILLUSTRATIVE PLOT FOR THIS SECTION}

@@

	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, right=4.33cm of mu] (MBobs) {$M_B$};
	% Survey nodes
	\node[latent, above=of sum, yshift=1cm,text width=2.7cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle,\rho,\sigma_{M_B}, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c, \kappa_0, \kappa_1$ };
	\node[latent, right=1.5cm of pop1, align=center] (sf) {$\Delta_i, \delta_i$};
	% Global nodes
	\node[latent, above=2cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=1.7cm of MBobs, text width=3cm, align=center]  (ab) {$\langle M_B \rangle, \alpha, \beta$, $\delta(0)$, \\$\delta(\infty)$, $\delta \mathcal{Z}_i$, $\delta S$};

@@

\begin{table}
	\centering
	\caption{Parameter Correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		%$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}

@@

Unfortunately, adding extra fit parameters to allow for shifting observables washes out cosmology, and applying a specific bias correction requires running a fiducial simulation (assuming cosmology, population and scatter model) and binning data. It is difficult to do whilst accounting for correlations with population and scatter model. This is compounded by the fact that bias corrections do not in general improve fits (increase the log posterior), and so are difficult to fit inherently. Works such as \citet{Kessler2017} show that bias corrections can be applied to supernovae datasets that can robustly handle multiple intrinsic scatter models, and future work will center on uniting these methodologies - incorporating better bias corrections that separate intrinsic scatter bias and non-Gaussian summary statistic bias from Malmquist bias, without having to precompute standardisation parameters and populations.

% Colour bias corrections for the {\celeven} scatter model are included in our cosmology model, the strengths of which are controlled by a fit parameter, $s_c$, however neither the {\gten} nor {\celeven} simulation fits constrained this parameter, and thus the majority of bias in the {\celeven} fits remain

\begin{figure*}
	\begin{center}
		\includegraphics[width=\textwidth]{bulk_cor.pdf}
	\end{center}
	\caption{Parameter correlations for the combined fits to the 100 {\gten} scatter model simulations. We see that the primary correlations with $w$ enter through $\alpha$, $\beta$ and $\langle M_B \rangle$, as shown in Table \ref{tab:parameter_correlations}. Also visible in this figure are several other interesting relationships. $\beta$ is strongly anti-correlated with intrinsic dispersion $\sigma_{m_B}$ for both surveys (DES like and LowZ), with $\sigma_{m_B}$ showing strong anti-correlation with $\kappa^0_c$. This relationship is indeed expected - as $\kappa^0_c$ grows larger (more unexplained dispersion on the colour observation), the width of the supernova population in apparent magnitude space increases. As the fit prefers it to conform to the observed width of the distribution, the extra width in colour causes the inherent magnitude smearing amount to decrease. And with extra freedom on the observed colour from $\kappa^0_c$, $\beta$ shifts in response. The other striking feature in the plot are the strong correlation blocks in the bottom right and the anti-correlation stripes on the edges. These too are expected, for they show the relationship between the colour distributions mean value, its width and its skewness. As skewness or population width increases, the effective mean of the population shifts (see Appendix \ref{app:approx} for details), creating anti-correlation between skewness and the (Gaussian) mean colour population. Strong anti-correlation between $\kappa_{c0}^0$ and $\kappa_{c0}^1$ with $\sigma_{m_B}$ reveals the strong population degeneracy, and -- for the C11 simulation results -- a constrained positive value shows that a finite non-zero extra colour dispersion is indeed preferred by our model. }
	\label{fig:bulk_cor}
\end{figure*}

Table \ref{tab:parameter_correlations} lists the fit correlations between our model fit parameters (excluding the LowZ band systematics, and Malmquist bias uncertainty parameters which had negligible correlation), showing (in order) cosmological parameters, standardisation parameters, population width and skewness parameters, intrinsic dispersion parameters, mass-step parameters, population mean parameters, SALT2 model systematics, dust systematic, global HST calibration systematic, peculiar velocity systematic, global redshift systematic and DES band magnitude and wavelength systematics. Figure \ref{fig:bulk_cor} show the full correlations between all non-systematic model parameters. As expected, $w$ bias would be introduced primarily through incorrectly determined standardisation parameters and mean absolute magnitude, which itself is tied to the unexplained colour dispersion and biases in colour introduced by the unknown intrinsic scatter model. Other interesting correlations are shown and discussed in Figure \ref{fig:bulk_cor}. The band systematics for DES filters $g$, $r$ and $i$ also show significant correlation with $w$, highlighting the importance of minimising instrumental uncertainty.

For the sample size of the DES and LowZ supernova samples (of order 350 supernova), the bias from intrinsic scatter models is sub-dominant to the statistical uncertainty, as shown in Figure \ref{fig:bulk_posterior}. {\green For our full systematics model, the bias represents a deviation between $0\sigma$ to $0.5\sigma$ depending on scatter model, and as such we will leave more complicated treatment of them for future work.}

@@

\citep{Scolnic2017}

@@

\begin{table}
	\centering
	\caption{Good table right here. Yeah boi.}
	\label{tab:bulk_summary_bbc}
	\begin{tabular}{l|ccc}
		\hline
		Model & {\gten} & {\celeven} & Mean ({\gten} + {\celeven}) \\
		\hline
		Steve $\langle w \rangle$           & $-0.998$ & $-0.945$ & $-1.010$ \\
		BBC $\langle w \rangle$             & $-1.044$ & $-0.978$ & $-0.972$ \\
		(Steve - BBC)  $\langle w \rangle$  & $-0.044$ & $-0.033$ & $-0.039$ \\
		\hline
		(Steve - BBC)  $\sigma_w$           & $0.057$ & $0.062$ & $0.060$ \\
		\hline
	\end{tabular}
\end{table}
